Finding Maximum $k$-Cliques Faster Using Lazy Global Domination

### 2016-05-23 paper/paper.tex
AAAIify

\usepackage{cleveref}
\usepackage{complexity}
\usepackage[ruled,vlined]{algorithm2e} % algorithms
\usepackage{booktabs}                  % less ugly tables
\usepackage[tight-spacing=true]{siunitx}
\usepackage{tikz}                      % For pretty pictures
\usepackage{gnuplot-lua-tikz}          % graphs

% \usepackage{showframe}

@@

% \input isn't expandable. yay.
\makeatletter\newcommand*\inputhaxx[1]{\@@input #1}\makeatother

@@

% drawing styles
\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.4cm, font=\small}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{selectedvertex/.style={vertex, fill=safedarkblue}}
\tikzset{delvertex/.style={vertex, dotted, color=safelightgrey}}
\tikzset{vertexc1/.style={vertex, fill=safelightblue}}
\tikzset{vertexc2/.style={vertex, fill=safedarkblue, text=safenearlywhite}}
\tikzset{vertexc3/.style={vertex, fill=safelightorange}}
\tikzset{vertexc4/.style={vertex, fill=safedarkorange, text=safenearlywhite}}

\tikzset{edge/.style={color=safelightgrey}}
\tikzset{bedge/.style={very thick}}
\tikzset{deledge/.style={dotted, color=safelightgrey}}
\tikzset{edgel1/.style={color=safeverydarkblue}}
\tikzset{edgel2/.style={color=safemediumorange}}
\tikzset{edgel3/.style={very thick, color=safedarkblue}}
\tikzset{edgel4/.style={very thick, color=safelightorange}}

\tikzset{processarrow/.style={->, very thick, decorate, decoration={snake, post length=0.5mm}}}
\tikzset{brace/.style={decorate, decoration={brace}, very thick}}
\tikzset{label/.style={font=\small}}

\makeatletter\@ifpackageloaded{showframe}{
    % show lines down the middle columns too
    % http://tex.stackexchange.com/questions/16199/test-if-a-package-or-package-option-is-loaded
\newlength\Fcolumnseprule\setlength\Fcolumnseprule{0.4pt}\def\@outputdblcol{%
  \if@firstcolumn\global \@firstcolumnfalse \global \setbox\@leftcolumn \box\@outputbox
  \else
    \global \@firstcolumntrue
    \setbox\@outputbox \vbox{\hb@xt@\textwidth{\hb@xt@\columnwidth{\box\@leftcolumn \hss}%
    \vrule \@width\Fcolumnseprule\hfil{\normalcolor\vrule \@width\columnseprule}
    \hfil\vrule \@width\Fcolumnseprule\hb@xt@\columnwidth {\box\@outputbox \hss}}}\@combinedblfloats\@outputpage
    \begingroup\@dblfloatplacement\@startdblcolumn\@whilesw\if@fcolmade \fi{\@outputpage\@startdblcolumn}\endgroup
  \fi
}}{}
\makeatother

\renewcommand{\topfraction}{0.9}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\dbltopfraction}{0.9}
\renewcommand{\textfraction}{0.05}
\setcounter{dbltopnumber}{2}
\renewcommand{\floatpagefraction}{0.85}
\renewcommand{\dblfloatpagefraction}{0.85}

% \frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Finding Maximum $k$-Cliques Faster Using Lazy Global Domination)
/Author (Ciaran McCreesh, Patrick Prosser)}
\setcounter{secnumdepth}{0}

@@

\begin{algorithm}[t]\DontPrintSemicolon
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (cvrej1c) at ($(pic cs:cvrej1) + (0, 0.15)$);
        \coordinate (cvrej2c) at ($(pic cs:cvrej2) + (0, 0.00)$);
        \node [fill=safelightblue, rounded corners, fit=(cvrej1c) (cvrej2c)] { };

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{5pt} % carefully tuned!
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-erdos}
    \bottomrule
\end{tabular}
\caption{Experimental results for Erd\H{o}s collaboration graphs. For each
graph, we consider $k$ equal to 2, 3 and 4. In each case we show the density of
$G^k$, the size of a maximum $k$-clique, and then for both the unmodified
algorithm and the algorithm with our lazy global domination step, the number of
nodes required, and the runtime in seconds.}\label{table:erdos}
\end{table}

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{5pt} % carefully tuned!
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-dimacs}
    \bottomrule
\end{tabular}
\caption{Experimental results for DIMACS clique graphs with diameter greater
    than two.}\label{table:clique}
\end{table}

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{3.5pt} % carefully tuned!
    \setlength{\aboverulesep}{-0.4pt} % this only affects the cmidrules on this table
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
        \cmidrule(lr){5-6} \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-dimacs10walshaw}
    \bottomrule
\end{tabular}
    \caption{Results for smaller DIMACS partitioning graphs.}\label{table:partitioning}
\end{table}

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{3.8pt} % carefully tuned!
    \setlength{\aboverulesep}{-0.4pt} % this only affects the cmidrules on this table
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-dimacs10cluster}
    \bottomrule
\end{tabular}
\caption{Results for smaller DIMACS clustering graphs.}\label{table:clustering}
\end{table}

@@

\begin{figure}[t]
    \centering
    \input{gen-graph-omega}
    \caption{Values of $\tilde{\omega}_k$ for random graphs $G(200, p)$, with varying edge probabilities.
        We see that even for very low edge probabilities, a maximum $k$-clique
    quickly covers the entire graph when $k > 1$.}
    \label{figure:graph-omega}
\end{figure}

\begin{figure}[t]
    \centering
    \input{gen-graph-nodes}
    \caption{Search space size for random graphs $G(200, p)^k$, with varying edge probabilities. We see that
        $4$-clique is easier than $3$-clique in practice, which in turn is easier than $2$-clique. (The
        complexity peak for maximum clique occurs at around edge probability 0.9, and requires
        approximately 15 million search nodes.)}
    \label{figure:graph-nodes}
\end{figure}

@@

>>>>

\usepackage{cleveref}                    % \cref
\usepackage{complexity}                  % \NP
\usepackage[ruled,vlined]{algorithm2e}   % algorithms
\usepackage{booktabs}                    % less ugly tables
\usepackage[tight-spacing=true]{siunitx} % formatting of units
\usepackage{tikz}                        % For pretty pictures
\usepackage{graphicx}                    % For the charts

@@

@@

% drawing styles
\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.4cm, font=\small}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{selectedvertex/.style={vertex, fill=safedarkblue}}
\tikzset{vertexc1/.style={vertex, fill=safelightblue}}
\tikzset{vertexc2/.style={vertex, fill=safedarkblue, text=safenearlywhite}}
\tikzset{vertexc3/.style={vertex, fill=safelightorange}}
\tikzset{vertexc4/.style={vertex, fill=safedarkorange, text=safenearlywhite}}
\tikzset{edge/.style={color=safelightgrey}}
\tikzset{bedge/.style={very thick}}
\tikzset{processarrow/.style={->, very thick, decorate, decoration={snake, post length=0.5mm}}}
\tikzset{brace/.style={decorate, decoration={brace}, very thick}}
\tikzset{label/.style={font=\small}}

\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Finding Maximum $k$-Cliques Faster Using Lazy Global Domination)
/Author (Ciaran McCreesh, Patrick Prosser)}
\setcounter{secnumdepth}{0}

@@

\begin{algorithm}[t!]\DontPrintSemicolon
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (cvrej1c) at ($(pic cs:cvrej1) + (0, 0.15)$);
        \coordinate (cvrej2c) at ($(pic cs:cvrej2) + (0, 0.00)$);
        \node [fill=safelightblue, rounded corners, fit=(cvrej1c) (cvrej2c)] { };

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{5pt} % carefully tuned!
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
Erdos971  & 2&0.09&42&42&0.0&42&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}472$& 3&0.31&117&121&0.0&119&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}1314$& 4&0.56&235&468&0.0&468&0.0\\
Erdos972  & 2&0.01&258&258&0.5&258&0.5\\
\hspace*{0.2em}\color{gray}$|V|{=}5488$& 3&0.09&517&537&0.8&521&0.8\\
\hspace*{0.2em}\color{gray}$|E|{=}8972$& 4&0.35&1509&\color{gray}\num{1.1e+07}&\color{gray}$>$ 1 h&8197&3.8\\
Erdos981  & 2&0.09&43&43&0.0&43&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}485$& 3&0.31&123&358&0.0&354&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}1381$& 4&0.57&245&246&0.0&246&0.0\\
Erdos982  & 2&0.01&274&274&0.6&274&0.6\\
\hspace*{0.2em}\color{gray}$|V|{=}5822$& 3&0.09&547&555&0.9&547&0.9\\
\hspace*{0.2em}\color{gray}$|E|{=}9505$& 4&0.35&1594&\color{gray}\num{1.1e+07}&\color{gray}$>$ 1 h&618826&207.3\\
Erdos991  & 2&0.09&43&44&0.0&44&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}492$& 3&0.31&126&375&0.0&374&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}1417$& 4&0.57&246&491&0.0&491&0.0\\
Erdos992  & 2&0.01&277&277&0.6&277&0.6\\
\hspace*{0.2em}\color{gray}$|V|{=}6100$& 3&0.09&562&573&0.9&562&0.8\\
\hspace*{0.2em}\color{gray}$|E|{=}9939$& 4&0.35&1643&\color{gray}\num{1.0e+07}&\color{gray}$>$ 1 h&202543&69.4\\
Erdos02  & 2&0.02&508&508&0.8&508&0.8\\
\hspace*{0.2em}\color{gray}$|V|{=}6927$& 3&0.20&1014&1022&1.3&1015&1.3\\
\hspace*{0.2em}\color{gray}$|E|{=}11850$& 4&1.00&6927&6927&11.9&6927&10.9\\
    \bottomrule
\end{tabular}
\caption{Experimental results for Erd\H{o}s collaboration graphs. For each
graph, we consider $k$ equal to 2, 3 and 4. In each case we show the density of
$G^k$, the size of a maximum $k$-clique, and then for both the unmodified
algorithm and the algorithm with our lazy global domination step, the number of
nodes required, and the runtime in seconds.}\label{table:erdos}
\end{table}

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{5pt} % carefully tuned!
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
c-fat200-1  & 2&0.13&18&41&0.0&35&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}200$& 3&0.19&24&74&0.0&48&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}1534$& 4&0.24&30&134&0.0&65&0.0\\
c-fat200-2  & 2&0.27&35&35&0.0&35&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}200$& 3&0.39&46&488&0.0&102&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}3235$& 4&0.50&57&1496&0.0&128&0.0\\
c-fat200-5  & 2&0.71&87&11513&0.0&257&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}200$& 3&1.00&200&200&0.0&200&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}8473$& 4&1.00&200&200&0.0&200&0.0\\
c-fat500-1  & 2&0.06&21&52&0.0&43&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}500$& 3&0.09&28&28&0.0&28&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}4459$& 4&0.11&35&35&0.0&35&0.0\\
c-fat500-2  & 2&0.12&39&134&0.0&79&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}500$& 3&0.17&52&52&0.0&52&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}9139$& 4&0.22&65&65&0.0&65&0.0\\
c-fat500-5  & 2&0.31&96&10133&0.1&196&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}500$& 3&0.44&128&128&0.1&128&0.1\\
\hspace*{0.2em}\color{gray}$|E|{=}23191$& 4&0.56&159&\color{gray}\num{1.5e+09}&\color{gray}$>$ 1 h&326&0.1\\
c-fat500-10  & 2&0.62&189&\color{gray}\num{1.1e+09}&\color{gray}$>$ 1 h&560&0.1\\
\hspace*{0.2em}\color{gray}$|V|{=}500$& 3&0.87&252&252&0.1&252&0.1\\
\hspace*{0.2em}\color{gray}$|E|{=}46627$& 4&1.00&500&500&0.1&500&0.1\\
p-hat300-1  & 2&1.00&299&299&0.0&299&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}300$& 3&1.00&300&300&0.1&300&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}10933$& 4&1.00&300&300&0.0&300&0.0\\
    \bottomrule
\end{tabular}
\caption{Experimental results for DIMACS clique graphs with diameter greater
    than two.}\label{table:clique}
\end{table}

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{3.5pt} % carefully tuned!
    % The following only affects the cmidrules on this table: by default booktabs sticks larger
    % spacing than normal latex tables do above and below mid-table rules. Usually that's fine, but
    % here the table is just slightly too large for the page, and I'd rather not use a smaller font
    % or cut one of the data points. (I suppose the other option would just be to just cut the
    % cmidrules out entirely, and then it fits perfectly...)
    \setlength{\aboverulesep}{-0.4pt}
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
        \cmidrule(lr){5-6} \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
3elt  & 2&0.00&10&340&0.3&340&0.6\\
\hspace*{0.2em}\color{gray}$|V|{=}4720$& 3&0.01&16&1582&0.4&1582&1.0\\
\hspace*{0.2em}\color{gray}$|E|{=}13722$& 4&0.01&27&911&0.4&911&0.7\\
4elt  & 2&0.00&11&486&3.8&486&5.5\\
\hspace*{0.2em}\color{gray}$|V|{=}15606$& 3&0.00&20&717&3.9&717&6.1\\
\hspace*{0.2em}\color{gray}$|E|{=}45878$& 4&0.00&36&345&3.9&345&4.4\\
add20  & 2&0.04&124&124&0.1&124&0.2\\
\hspace*{0.2em}\color{gray}$|V|{=}2395$& 3&0.25&671&671&0.2&671&0.2\\
\hspace*{0.2em}\color{gray}$|E|{=}7462$& 4&0.67&1454&1454&0.5&1454&0.5\\
add32  & 2&0.00&32&32&0.4&32&0.4\\
\hspace*{0.2em}\color{gray}$|V|{=}4960$& 3&0.01&99&286&0.4&194&0.4\\
\hspace*{0.2em}\color{gray}$|E|{=}9462$& 4&0.03&268&268&0.4&268&0.5\\
bcsstk29  & 2&0.01&72&9752&3.7&963&8.7\\
\hspace*{0.2em}\color{gray}$|V|{=}13992$& 3&0.02&132&\num{2.7e+07}&1576.2&7781&11.4\\
\hspace*{0.2em}\color{gray}$|E|{=}302748$& 4&0.04&210&\color{gray}\num{3.2e+07}&\color{gray}$>$ 1 h&21689&16.9\\
bcsstk30  & 2&0.01&219&224&14.5&219&14.5\\
\hspace*{0.2em}\color{gray}$|V|{=}28924$& 3&0.03&496&509&17.8&496&17.6\\
\hspace*{0.2em}\color{gray}$|E|{=}1007284$& 4&0.05&843&854&23.7&845&23.3\\
bcsstk31  & 2&0.00&189&189&20.2&189&20.0\\
\hspace*{0.2em}\color{gray}$|V|{=}35588$& 3&0.01&278&605&21.8&369&22.8\\
\hspace*{0.2em}\color{gray}$|E|{=}572914$& 4&0.02&428&119640&97.9&6588&29.8\\
bcsstk33  & 2&0.03&141&141&1.3&141&1.3\\
\hspace*{0.2em}\color{gray}$|V|{=}8738$& 3&0.08&228&26033&6.3&1744&3.8\\
\hspace*{0.2em}\color{gray}$|E|{=}291583$& 4&0.15&435&\num{2.0e+06}&380.4&52779&17.6\\
crack  & 2&0.00&10&2894&1.5&2894&7.8\\
\hspace*{0.2em}\color{gray}$|V|{=}10240$& 3&0.00&17&4996&1.7&4987&10.4\\
\hspace*{0.2em}\color{gray}$|E|{=}30380$& 4&0.01&31&2173&1.7&2173&7.0\\
cs4  & 2&0.00&6&5780&8.2&5780&73.4\\
\hspace*{0.2em}\color{gray}$|V|{=}22499$& 3&0.00&12&7812&8.4&7812&78.5\\
\hspace*{0.2em}\color{gray}$|E|{=}43858$& 4&0.00&18&29032&9.5&29032&136.3\\
cti  & 2&0.00&7&8918&4.5&8918&58.0\\
\hspace*{0.2em}\color{gray}$|V|{=}16840$& 3&0.00&15&6406&4.8&6406&45.5\\
\hspace*{0.2em}\color{gray}$|E|{=}48232$& 4&0.01&26&62316&7.0&62316&113.6\\
data  & 2&0.01&18&638&0.1&617&0.2\\
\hspace*{0.2em}\color{gray}$|V|{=}2851$& 3&0.02&32&4982&0.1&4913&0.2\\
\hspace*{0.2em}\color{gray}$|E|{=}15093$& 4&0.04&52&40095&0.4&36089&0.4\\
fe-4elt2  & 2&0.00&13&61&1.7&61&2.1\\
\hspace*{0.2em}\color{gray}$|V|{=}11143$& 3&0.00&20&389&1.8&389&3.0\\
\hspace*{0.2em}\color{gray}$|E|{=}32818$& 4&0.01&32&448&1.8&446&3.0\\
fe-pwt  & 2&0.00&16&95&21.8&95&22.6\\
\hspace*{0.2em}\color{gray}$|V|{=}36519$& 3&0.00&29&167&21.0&167&24.4\\
\hspace*{0.2em}\color{gray}$|E|{=}144794$& 4&0.00&52&224&21.1&224&23.9\\
fe-sphere  & 2&0.00&7&14173&4.5&14173&53.0\\
\hspace*{0.2em}\color{gray}$|V|{=}16386$& 3&0.00&12&34328&4.9&34328&111.1\\
\hspace*{0.2em}\color{gray}$|E|{=}49152$& 4&0.00&19&73632&6.3&73632&148.7\\
memplus  & 2&0.02&574&574&5.8&574&5.7\\
\hspace*{0.2em}\color{gray}$|V|{=}17758$& 3&0.26&8057&8061&49.4&8058&48.2\\
\hspace*{0.2em}\color{gray}$|E|{=}54196$& 4&0.74&8963&8963&95.5&8963&92.4\\
uk  & 2&0.00&5&433&0.3&433&0.7\\
\hspace*{0.2em}\color{gray}$|V|{=}4824$& 3&0.00&8&1891&0.4&1891&0.9\\
\hspace*{0.2em}\color{gray}$|E|{=}6837$& 4&0.01&14&2168&0.4&2168&1.0\\
vibrobox  & 2&0.02&121&302&2.9&302&3.5\\
\hspace*{0.2em}\color{gray}$|V|{=}12328$& 3&0.08&408&1984&8.9&1984&10.0\\
\hspace*{0.2em}\color{gray}$|E|{=}165250$& 4&0.26&${\ge}1094$&\color{gray}\num{7.9e+06}&\color{gray}$>$ 1 h&\color{gray}\num{7.4e+06}&\color{gray}$>$ 1 h\\
whitaker3  & 2&0.00&9&1222&1.3&1222&4.8\\
\hspace*{0.2em}\color{gray}$|V|{=}9800$& 3&0.00&15&3724&1.4&3724&7.4\\
\hspace*{0.2em}\color{gray}$|E|{=}28989$& 4&0.01&23&6530&1.5&6530&9.5\\
wing-nodal  & 2&0.01&29&648&2.1&648&3.5\\
\hspace*{0.2em}\color{gray}$|V|{=}10937$& 3&0.02&54&13091&4.2&13039&15.2\\
\hspace*{0.2em}\color{gray}$|E|{=}75488$& 4&0.04&114&\num{6.0e+07}&1981.3&\num{6.0e+07}&1908.9\\
    \bottomrule
\end{tabular}
    \caption{Results for smaller DIMACS partitioning graphs.}\label{table:partitioning}
\end{table}

@@

\begin{table}
    \scriptsize\setlength{\tabcolsep}{3.8pt} % carefully tuned!
    % The following only affects the cmidrules on this table: by default booktabs sticks larger
    % spacing than normal latex tables do above and below mid-table rules. Usually that's fine, but
    % here the table is just slightly too large for the page, and I'd rather not use a smaller font
    % or cut one of the data points. (I suppose the other option would just be to just cut the
    % cmidrules out entirely, and then it fits perfectly...)
    \setlength{\aboverulesep}{-0.4pt}
    \centering
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
adjnoun  & 2&0.50&50&50&0.0&50&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}112$& 3&0.91&83&164&0.0&164&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}425$& 4&0.99&107&107&0.0&107&0.0\\
as-22july06  & 2&0.04&2391&2391&11.7&2391&11.3\\
\hspace*{0.2em}\color{gray}$|V|{=}22963$& 3&0.36&8455&\color{gray}374427&\color{gray}$>$ 1 h&94497&898.2\\
\hspace*{0.2em}\color{gray}$|E|{=}48436$& 4&0.79&14911&14911&252.0&14911&250.4\\
astro-ph  & 2&0.01&361&365&5.0&362&5.0\\
\hspace*{0.2em}\color{gray}$|V|{=}16706$& 3&0.10&1553&1567&15.3&1560&12.5\\
\hspace*{0.2em}\color{gray}$|E|{=}121251$& 4&0.35&${\ge}4040$&\color{gray}\num{1.0e+06}&\color{gray}$>$ 1 h&\color{gray}\num{1.1e+06}&\color{gray}$>$ 1 h\\
celegans-meta  & 2&0.44&238&238&0.0&238&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}453$& 3&0.89&371&371&0.0&371&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}2025$& 4&0.98&432&432&0.0&432&0.0\\
celegansneural  & 2&0.55&135&135&0.0&135&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}297$& 3&0.95&245&245&0.0&245&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}2148$& 4&1.00&295&295&0.0&295&0.0\\
cond-mat  & 2&0.00&108&108&4.5&108&4.5\\
\hspace*{0.2em}\color{gray}$|V|{=}16726$& 3&0.01&250&1403&5.1&844&5.6\\
\hspace*{0.2em}\color{gray}$|E|{=}47594$& 4&0.05&720&\color{gray}\num{7.3e+06}&\color{gray}$>$ 1 h&674453&280.6\\
cond-mat-2003  & 2&0.00&203&204&15.7&204&16.0\\
\hspace*{0.2em}\color{gray}$|V|{=}31163$& 3&0.02&${\ge}629$&\color{gray}\num{6.3e+06}&\color{gray}$>$ 1 h&\color{gray}\num{6.1e+06}&\color{gray}$>$ 1 h\\
\hspace*{0.2em}\color{gray}$|E|{=}120029$& 4&0.12&${\ge}2605$&\color{gray}\num{1.9e+06}&\color{gray}$>$ 1 h&\color{gray}\num{1.8e+06}&\color{gray}$>$ 1 h\\
cond-mat-2005  & 2&0.00&279&279&26.8&279&26.4\\
\hspace*{0.2em}\color{gray}$|V|{=}40421$& 3&0.03&${\ge}1060$&\color{gray}\num{2.0e+06}&\color{gray}$>$ 1 h&\color{gray}\num{1.9e+06}&\color{gray}$>$ 1 h\\
\hspace*{0.2em}\color{gray}$|E|{=}175691$& 4&0.16&${\ge}4185$&\color{gray}562816&\color{gray}$>$ 1 h&\color{gray}585596&\color{gray}$>$ 1 h\\
dolphins  & 2&0.32&14&14&0.0&14&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}62$& 3&0.59&30&30&0.0&30&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}159$& 4&0.77&40&40&0.0&40&0.0\\
email  & 2&0.09&72&72&0.0&72&0.1\\
\hspace*{0.2em}\color{gray}$|V|{=}1133$& 3&0.45&233&19031&0.3&19031&0.4\\
\hspace*{0.2em}\color{gray}$|E|{=}5451$& 4&0.86&654&6854&0.3&6676&0.4\\
football  & 2&0.45&17&147&0.0&145&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}115$& 3&0.95&69&70&0.0&70&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}613$& 4&1.00&115&115&0.0&115&0.0\\
hep-th  & 2&0.00&51&51&1.0&51&1.0\\
\hspace*{0.2em}\color{gray}$|V|{=}8361$& 3&0.01&125&239&1.2&176&1.3\\
\hspace*{0.2em}\color{gray}$|E|{=}15751$& 4&0.04&347&158164&21.6&23714&4.7\\
jazz  & 2&0.69&103&107&0.0&107&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}198$& 3&0.95&174&174&0.0&174&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}2742$& 4&0.99&192&192&0.0&192&0.0\\
karate  & 2&0.61&18&18&0.0&18&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}34$& 3&0.86&25&25&0.0&25&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}78$& 4&0.99&33&33&0.0&33&0.0\\
lesmis  & 2&0.43&37&37&0.0&37&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}77$& 3&0.85&58&58&0.0&58&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}254$& 4&0.99&75&75&0.0&75&0.0\\
netscience  & 2&0.01&35&35&0.0&35&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}1589$& 3&0.01&54&54&0.0&54&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}2742$& 4&0.02&85&85&0.0&85&0.0\\
PGPgiantcompo  & 2&0.00&206&206&1.7&206&1.7\\
\hspace*{0.2em}\color{gray}$|V|{=}10680$& 3&0.02&423&843&2.6&841&2.7\\
\hspace*{0.2em}\color{gray}$|E|{=}24316$& 4&0.07&1161&1161&5.9&1161&6.0\\
polblogs  & 2&0.27&352&352&0.1&352&0.1\\
\hspace*{0.2em}\color{gray}$|V|{=}1490$& 3&0.58&776&2210&1.2&2177&1.2\\
\hspace*{0.2em}\color{gray}$|E|{=}16715$& 4&0.66&1127&1537&2.0&1166&1.9\\
polbooks  & 2&0.37&28&28&0.0&28&0.0\\
\hspace*{0.2em}\color{gray}$|V|{=}105$& 3&0.64&54&54&0.0&54&0.0\\
\hspace*{0.2em}\color{gray}$|E|{=}441$& 4&0.86&68&68&0.0&68&0.0\\
power  & 2&0.00&20&20&0.4&20&0.4\\
\hspace*{0.2em}\color{gray}$|V|{=}4941$& 3&0.00&30&30&0.4&30&0.4\\
\hspace*{0.2em}\color{gray}$|E|{=}6594$& 4&0.01&61&61&0.4&61&0.4\\
    \bottomrule
\end{tabular}
\caption{Results for smaller DIMACS clustering graphs.}\label{table:clustering}
\end{table}

@@

\begin{figure}[h!] % try to keep this immediately above the next figure
    \centering
    \includegraphics{gen-graph-omega.pdf}
    \caption{Values of $\tilde{\omega}_k$ for random graphs $G(200, p)$, with varying edge probabilities.
        We see that even for very low edge probabilities, a maximum $k$-clique
    quickly covers the entire graph when $k > 1$.}
    \label{figure:graph-omega}
\end{figure}

\begin{figure}[h!] % try to keep this immediately below the previous figure
    \centering
    \includegraphics{gen-graph-nodes.pdf}
    \caption{Search space size for random graphs $G(200, p)^k$, with varying edge probabilities. We see that
        $4$-clique is easier than $3$-clique in practice, which in turn is easier than $2$-clique. (The
        complexity peak for maximum clique occurs at around edge probability 0.9, and requires
        approximately 15 million search nodes.)}
    \label{figure:graph-nodes}
\end{figure}

@@

\begin{figure}[h!] % try to keep this immediately above the next figure
    \centering
    \includegraphics{gen-graph-omega-2.pdf}
    \caption{The size of a maximum $2$-clique in random graphs $G(n, p)$ with varying edge
        probabilities, and different values of $n$. For $G(50, p)$, a $2$-clique has size average 50
    from $p = 0.42$ onwards.}
    \label{figure:graph-omega-2}
\end{figure}
